Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-07-22 MSc-dissertation.tex
New structure

\section{Parameter estimation}

[implementation details and options/ settings that are affecting the ABC]

@@

\subsection{ABC SMC and model hyperparameters experiments}

@@

\subsubsection{Perturbation kernels}

@@

\paragraph{Conclusion} Local kernels can be fast bur unstable in some case; for a general parameter inference of our models, multivariate kernels are preferred, as a good fit is our prior target; some local kernels are also worth trying after the multivariate normal kernel, e.g. local M-NN with M$\leq 250$ (for population size of 2000, i.e. 12.5\% of the population) and multivariate normal with scaling. Also multivariate M-NN is worth trying, although it is not built in \verb|pyABC| and requires additional implementations.

@@

\subsubsection{Adaptive functions and factors}

@@

\paragraph{Conclusion} We noticed the significant efficiency improvement of these adaptive options; they can largely improve the acceptance rate in some cases. However, as the factors and weights are directly multiplied to $\Delta x$ and thus the metrics for distance are changed, a direct compare of the efficiency under the same threshold schedule is unfeasible; after the same number of generations they can reach a small $\epsilon_t$ but still the approximated posterior is not as accurate as the standard implementation. AS a result, our implementation of the parameter inference will only consider standard distance function and factors are only tested for improvements (FIGURE).

\subsubsection{Data size, prior distribution range, population size and generations}

@@

\paragraph{Summary} This subsection aims to preliminarily explore ABC SMC settings using synthetic data with known true parameter values, thus the efficiency and the goodness of the resultant model can be compared across these options. Conclusion can be drawn to choose efficient and proper options of ABC SMC to be applied on the target models with experimental data. It also provides reference for a general inference task using SMC with high dimensional parameter space.

\section{Model comparison}

[comparison of model 1, 2 and 3]

@@

\section{Performance experiments}

@@

\subsection{Scaling-up}

@@

\subsection{Profiling}

@@

@@

\section{Performance experiments}

>>>>

% \section{Parameter estimation}

% [implementation details and options/ settings that are affecting the ABC]

\section{ABC SMC and model hyperparameters experiments}

@@

@@

\subsection{Perturbation kernels}

@@

\subsubsection{Conclusion} Local kernels can be fast bur unstable in some case; for a general parameter inference of our models, multivariate kernels are preferred, as a good fit is our prior target; some local kernels are also worth trying after the multivariate normal kernel, e.g. local M-NN with M$\leq 250$ (for population size of 2000, i.e. 12.5\% of the population) and multivariate normal with scaling. Also multivariate M-NN is worth trying, although it is not built in \verb|pyABC| and requires additional implementations.

@@

\subsection{Adaptive functions and factors}

@@

\subsubsection{Conclusion} We noticed the significant efficiency improvement of these adaptive options; they can largely improve the acceptance rate in some cases. However, as the factors and weights are directly multiplied to $\Delta x$ and thus the metrics for distance are changed, a direct compare of the efficiency under the same threshold schedule is unfeasible; after the same number of generations they can reach a small $\epsilon_t$ but still the approximated posterior is not as accurate as the standard implementation. AS a result, our implementation of the parameter inference will only consider standard distance function and factors are only tested for improvements (FIGURE).

\subsection{Data size, prior distribution range, population size and generations}

@@

\subsubsection{Summary} This subsection aims to preliminarily explore ABC SMC settings using synthetic data with known true parameter values, thus the efficiency and the goodness of the resultant model can be compared across these options. Conclusion can be drawn to choose efficient and proper options of ABC SMC to be applied on the target models with experimental data. It also provides reference for a general inference task using SMC with high dimensional parameter space.

\section{Parameter estimation and model comparison}

[separated ABC run on model 1, 2 and 3]

[model comparison among model 1, 2, 3]

[features that derive model 4 and 5]

@@

\chapter{Performance experiments}

@@

\section{Scaling-up}

@@

\subsubsection{Results}

\section{Profiling}

@@

\subsubsection{Results}

@@
